Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 result_discussion.tex
resolving some easy edits

Our algorithm's payment is constant in $T$,
while its regret is $O(\log^3(T))$ in general with a lower bound of
$\Omega(\log(T))$;
when preferences are discrete, our algorithm's regret is
constant in $T$.
Thus, viewed solely in terms of the dependence on $T$,
the best performance achievable seems comparable to that in a standard
multi-armed bandit problem;
but when preferences are discrete, the constant regret
surpasses the $\Theta(\log(T))$ achievable in the standard multi-armed
bandit \dkedit{setting}.
This may seem surprising, because the principal in our setting has
both less control and less information than in the standard bandit setting.
The result arises because heterogeneity in preferences provides
free exploration, and allows all of the arms to be pulled infinitely
often without incurring regret once estimates are accurate enough.

>>>>

Our algorithm's payment is constant in $T$,
while its regret is $O(\log^3(T))$ in general with a lower bound of
$\Omega(\log(T))$;
when preferences are discrete, our algorithm's regret is
constant in $T$.
Thus, viewed solely in terms of the dependence on $T$,
the best performance achievable seems comparable to that in a standard
multi-armed bandit problem;
but when preferences are discrete, the constant regret
surpasses the $\Theta(\log(T))$ achievable in the standard multi-armed
bandit setting.
This may seem surprising, because the principal in our setting has
both less control and less information than in the standard bandit setting.
The result arises because heterogeneity in preferences provides
free exploration, and allows all of the arms to be pulled infinitely
often without incurring regret once estimates are accurate enough.
